|

### 2021-02-01 appendix/appendix.Rmd
finish experiment 01

In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
R\$5,0001 to R\$10,000 per month (US\$920 to US\$1840 as of January 2021), which
comprise the largest group in our sample. However, the sample also contains
`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
and R\$2,000 (US\$ 185 to US\$370) and `r df2[7, 3]*100`% with household incomes
up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
this respect, we have reached participants from all social classes.

@@

# Tables
mm_college <- mm_by %>% filter(BY == "College")
table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
mm_grad <- mm_by %>% filter(BY == "Graduate School")
table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
mm_high <- mm_by %>% filter(BY == "High School")
table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
```
\normalsize

@@

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Income)

@@

>>>>

In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
comprise the largest group in our sample. However, the sample also contains
`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
and R\$2,000 (US\$ 184 to US\$368) and `r df2[7, 3]*100`% with household incomes
up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
this respect, we have reached participants from all social classes.

@@

# Tables
mm_college <- mm_by %>% filter(BY == "College")
table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
mm_grad <- mm_by %>% filter(BY == "Graduate School")
table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
mm_high <- mm_by %>% filter(BY == "High School")
table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
```

```{r conjoint-degree, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
```
\normalsize

@@

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable difference amongst them.

\footnotesize
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Income)

@@

### Support for Death Penalty

Here we assess whether subjects who support the death penalty have different
preferences towards lynching victims. There are fewer respondents who answered
"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
from their estimates are larger than the for the other two categories. The
estimates largely overlap across the four groups, although those who answered "Rather Not Say" are less favorable to lynching Indigenous criminals.

\footnotesize
```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(death_penalty)
cjdt$death_penalty <- factor(cjdt$death_penalty)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~death_penalty)

plot(mm_by, group = "death_penalty", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_dk <- mm_by %>% filter(BY == "Don't Know")
table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
```

```{r conjoint-deathrns, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
```

```{r conjoint-deathyes, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
```

\normalsize

### Previous Victimization

Respondents who had been victimized in the past 12 months also do not have
different preferences towards lynchings victim profiles. The results are
virtually identical for both groups, as one can see below.

```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id")
cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)

mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Previous_Victim)

# Plot
plot(mm_by, group = "Previous_Victim", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_no <- mm_by %>% filter(BY == "No")
table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
```

```{r conjoint-victimizationyes, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_yes <- mm_by %>% filter(BY == "Yes")
table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
```
\normalsize

### Opinion on the Police

Experimental results do not change when we break the responses according to how
subjects view the police forces.

\footnotesize
```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
                                   views_police == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_police)) %>% drop_na(views_police2)
cjdt$Police <- factor(cjdt$views_police2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Police)

# Plot
plot(mm_by, group = "Police", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
```

```{r conjoint-polvbad, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
```
\newpage

```{r conjoint-polvgood, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
```
\normalsize

### Opinion on the Judicial System

Lastly, we analyze whether personal beliefs about the judicial system affect
the type of lynching victim respondents select.

\footnotesize
```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
                                   views_justice == "Don't Know" ~ NA_character_,
                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
cjdt$Judiciary <- factor(cjdt$views_justice2)

mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", 
            h0 = 0.5, by = ~Judiciary)

# Plot
plot(mm_by, group = "Judiciary", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_bad <- mm_by %>% filter(BY == "Bad")
table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
mm_good <- mm_by %>% filter(BY == "Good")
table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
mm_regular <- mm_by %>% filter(BY == "Regular")
table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
```

```{r conjoint-justicevbad, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_vbad <- mm_by %>% filter(BY == "Very Bad")
table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
```

```{r conjoint-justicevgood, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_vgood <- mm_by %>% filter(BY == "Very Good")
table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
```
\normalsize

# Experiment 02
